Reanalysis Step 2: Multiple Imputation

### 2025-08-19 reanalysis-2-multiple_imputation.qmd
debug

# ANALYSIS MODE: "test" or "final"
# test = 2 imputations, 5 iterations (fast)
# final = 30 imputations, 20 iterations (slow but thorough)
analysis_mode <- "final"  # Change to "final" for production run

# Set parameters based on mode
if (analysis_mode == "test") {
  n_imputations <- 2
  n_iterations <- 5
  message("Running in TEST mode: ", n_imputations, " imputations, ", n_iterations, " iterations")
} else if (analysis_mode == "final") {
  n_imputations <- 10
  n_iterations <- 20
  message("Running in FINAL mode: ", n_imputations, " imputations, ", n_iterations, " iterations")
} else {
  stop("Invalid analysis_mode. Must be 'test' or 'final'")
}
```

@@

# Print model parameters
message("=== IMPUTATION PARAMETERS ===")
message("Mode: ", analysis_mode)
message("Number of imputations (m): ", n_imputations)
message("Max iterations per imputation (maxit): ", n_iterations)
message("Random seed: 2025")
```

@@

# Verify completeness
completeness_check <- lapply(imputed_datasets, function(d) {
  sum(!complete.cases(d[, ps_model_vars]))
})

>>>>

# ANALYSIS MODE: "test" or "final"
# test = 2 imputations, 5 iterations (fast)
# final = 30 imputations, 20 iterations (slow but thorough)
analysis_mode <- "test"  # Change to "final" for production run

# Set parameters based on mode
if (analysis_mode == "test") {
  n_imputations <- 2
  n_iterations <- 2
  message("Running in TEST mode: ", n_imputations, " imputations, ", n_iterations, " iterations")
} else if (analysis_mode == "final") {
  n_imputations <- 10
  n_iterations <- 20
  message("Running in FINAL mode: ", n_imputations, " imputations, ", n_iterations, " iterations")
} else {
  stop("Invalid analysis_mode. Must be 'test' or 'final'")
}
```

@@

# Print model parameters
message("Imputation Parameters:")
message("Mode: ", analysis_mode)
message("Number of imputations (m): ", n_imputations)
message("Max iterations per imputation (maxit): ", n_iterations)
message(paste("Random seed: ", seed))
```

@@

completeness_check <- lapply(imputed_datasets, function(d) {
  sum(!complete.cases(d[, ps_model_vars]))
})
